Toward dynamic models of combat or lack thereof in animal mating

### 2016-02-13 ms.tex
fixed bug with cts contests

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_pc_plot_cts.pdf}
    \caption{New cts contests. Percent energy expenditure of cohort at generation 499}
    \label{fig:var energy pc}
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_total_plot_cts.pdf}
    \caption{New cts contests, Total energy expenditure of cohort at generation 499}
    \label{fig:var energy total}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/cts_k_density.pdf}
    \caption{New cts contests a density plot of the aggression parameter k at max energy, ie $\alpha$}
    \label{fig:var k density}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/cts_e_0_density.pdf}
    \caption{ New cts contests a density plot of the aggression parameter $e_0$ at max energy, ie $\beta$,
    commitment = $\alpha \Delta \bar{M} + \beta$ }
    \label{fig:var e_0 density}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/cts_k_history.pdf}
    \caption{New cts contests, k ie $\alpha$}
    \label{fig:k history}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/cts_e_0_history.pdf}
    \caption{New cts contests,  e 0 ie $\beta$}
    \label{fig:e_0 history}
\end{figure}
